This is the Title

### 2017-03-15 abc/paper/paper.tex
Point out the spot that keeps getting relocated. This changes the string, which maybe makes a flower joke/misdirection possible?

Thank you for playing wing commander.

@@

style points for:
- put relocations a little later after CS, so that we can mark
  with text the spot where they go.

@@

 NEED TO FIX:
  - some kind of output other than \_putc

@@

dosbox patches, wing commander

@@

ascii art in paper

@@

@@

>>>>

@@

@@

@@

@@

@@

songs to do: https://www.youtube.com/watch?v=EJkJbUbvYJA

@@

could write about optimizing the value table
